Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-01-27 ms.tex
more

\begin{figure}
\includegraphics[width=\columnwidth]{vwSources.pdf}
\caption{\label{fig:vwSources} $\vwO$ for stellar winds ({\it solid
    blue}), SNe Ia ({\it dashed red}), MSPs ({\it solid orange}), as a
  function of $\Mbh$. Each heating source varies with the star
  formation history, which is a function of $\Mbh$--see
  appendix~\ref{app:windheat} for the detailed description of how we
  calculate $\vwO$ as a function of $\Mbh$. We also show the $\vwO$,
  resulting from stellar winds, MSPs, and black hole feedback ({\it
    solid black}). The heating will have a weak dependence on the
  stellar density power law slope, $\Gamma$, since $v_{w}^{\bullet \,
    2}$ depends on $\Gamma$. The solid black curve corresponds to
  $\Gamma=0.8$ and the dash-dotted black curve corresponds to
  $\Gamma=0.1$. Finally the vertical dashed black line marks the value
  critical value of $\Mbh$, $M_{\rm bh, crit}$, such that... }
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{eta.pdf}
\caption{\label{fig:eta} Parameter characterizing stellar mass loss $\eta$ (eq.~[\ref{eq:q}]) as a function of black hole mass $\Mbh$, calculated for average star formation histories corresponding to galaxies with halo masses corresponding to $\Mbh$ according to the results of \citet{MosterNaab+:2013a}. }
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{vwSources.pdf}
\caption{\label{fig:vwSources} Sources contributing to the heating rate of the CNM, $\vwO$, including stellar wind heating ({\it solid blue}), Ia supernovae ({\it dashed red}), millisecond pulsars ({\it solid orange}).  Each heating source varies with black hole mass $\Mbh$ due to the different average star formation history of galaxies of a given halo mass (see Appendix~\ref{app:windheat} for the detailed description).   We assume a stellar density power law slope of $\Gamma = 0.8$ in calculating $v_{w}^{\bullet \, 2}$ although the dependence on $\Gamma$ is weak {\bf BDM: just pick a value of Gamma!}.  The Ia heating rate is shown as a solid above the critical black hole mass for which $r_{\rm Ia} < r_{\rm s}$ (Fig.~\ref{fig:rs_rIa}), since this represents the condition for SN Ia to be well-approximated a continuously heating source. }
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{eta.pdf}
\caption{\label{fig:eta} Parameter  $\eta$ characterizing stellar mass loss rate (eq.~[\ref{eq:q}]) as a function of black hole mass $\Mbh$, calculated for average star formation histories from \citet{MosterNaab+:2013a} for galaxies with halo masses corresponding to $\Mbh$. }
\end{figure}
